---
title: "analysis_industry_fe"
output: html_document
date: "2024-03-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plm)
library(lfe)
library(fixest)
library(lme4)
library(pglm)
library(dplyr)
library(tidyr)
library(stargazer)
library(ggplot2)
```

# READ-IN DATA
bpl_dict ={'cambodia': 51100, 'iran':53000, 'iraq':53200,'somalia':60050,'poland':45500,'romania':4560, 'ethiopia':60044,
            'cuba': 25000, 'yugoslavia':45700,'laos':51300, 'ussr':46500,'vietnam':51800, 'afghanistan': 52000}
```{r}
df <- read.csv("sample_ind_IV_full.csv",header=TRUE)
df <- within(df, {
  never_married <- factor(never_married)
  CBSA10 <- factor(CBSA10)
  reg_yr <- factor(reg_yr)
  ind_yr <- factor(ind_yr)
  industry <- factor(industry)
  STATE10 <- factor(STATE10)
  year <- factor(year)
  age_sqrd <- age^2
  count_cbsa <- count_cbsa/10^4 # in ten thousands
  IV_ct <- IV_ct/10^4 # in ten thousands
  IV_d_ct <- IV_d_ct/10^4 # in ten thousands
  count_cbsa_asinh <- asinh(count_cbsa)
  IV_ct_asinh <- asinh(IV_ct)
  IV_d_ct_asinh <- asinh(IV_d_ct)
  log_hrs_work <- log(hrs_work)
})
```



# Female sample
```{r}
df_sample <- df %>% filter(sex1968==2)
table(df_sample$occupation)
stargazer(df_sample, type="latex", title="Summary Statistics", digits=2)
```

```{r}
summary(df_sample %>% count(year))
```

# employment
## employed

```{r}
df_sample_employed <- df_sample %>% drop_na(c(count_cbsa, age, age_sqrd, white,
                                              never_married, IV_ct, CBSA10,edu, 
                                              reg_yr, industry, ind_yr, employed))
```

```{r}
# without transformation 
employed_logit0  <- feglm(employed ~ count_cbsa | CBSA10 + reg_yr  + ind_yr,  family=binomial(), data=df_sample_employed)
summary(employed_logit0, cluster = "CBSA10")
```

```{r}
# with inverse hyperbolic sine transformation 
employed_logit0_asinh  <- feglm(employed ~ count_cbsa_asinh | CBSA10 + reg_yr  + ind_yr, 
                                family=binomial(), data=df_sample_employed)
summary(employed_logit0, cluster = "CBSA10")
```


```{r}
# without transformation 
employed_linear0 <- felm(employed ~ count_cbsa|CBSA10 + reg_yr + ind_yr|0|CBSA10,data=df_sample_employed)
summary(employed_linear0)
```

```{r}
# without transformation 
employed_logit1 <-feglm(employed ~ count_cbsa + age + age_sqrd + never_married + edu + white| CBSA10 + reg_yr  + ind_yr, family=binomial(), data=df_sample_employed)
summary(employed_logit1, cluster = "CBSA10")
```

```{r}
# without transformation 
employed_linear1 <- felm(employed ~ count_cbsa + age + age_sqrd + never_married + edu+white|CBSA10+reg_yr + ind_yr|0|CBSA10,data=df_sample_employed)
summary(employed_linear1)
```

## temp_off

```{r}
df_sample_temp_off <- df_sample %>% drop_na(c(count_cbsa, age,  age_sqrd, white,
                                              never_married, IV_ct, CBSA10, edu, 
                                              reg_yr, temp_off, industry, ind_yr))
```

```{r}
# without transformation 
temp_off_logit0  <- feglm(temp_off ~ count_cbsa | CBSA10 + reg_yr + ind_yr, family=binomial(), data=df_sample_temp_off)
summary(temp_off_logit0, cluster = "CBSA10")
```

```{r}
# with inverse hyperbolic sine transformation 
temp_off_logit0_asinh  <- feglm(temp_off ~ count_cbsa_asinh | CBSA10 + reg_yr + ind_yr, 
                                family=binomial(), data=df_sample_temp_off)
summary(temp_off_logit0, cluster = "CBSA10")
```


```{r}
# without transformation 
temp_off_linear0 <- felm(temp_off ~ count_cbsa|CBSA10 + reg_yr + ind_yr|0|CBSA10,data=df_sample_temp_off)
summary(temp_off_linear0)
```

```{r}
# without transformation 
temp_off_logit1 <-feglm(temp_off ~ count_cbsa + age + age_sqrd + never_married + edu | CBSA10 + reg_yr + ind_yr, family=binomial(), data=df_sample_temp_off)
summary(temp_off_logit1, cluster = "CBSA10")
```

```{r}
# without transformation 
temp_off_linear1 <- felm(temp_off ~ count_cbsa + age + age_sqrd + never_married + edu+white|CBSA10+reg_yr + ind_yr|0|CBSA10,data=df_sample_temp_off)
summary(temp_off_linear1)
```


## unemployed
### regardless of industry affiliation
```{r}
df_sample_unemployed_full <- df_sample %>% drop_na(c(count_cbsa, age,  age_sqrd, white,
                                              never_married, IV_ct, CBSA10, edu, 
                                              reg_yr, unemployed))
```

```{r}
# without transformation 
unemployed_logit0  <- feglm(unemployed ~ count_cbsa | CBSA10 + reg_yr, family=binomial(), data=df_sample_unemployed_full)
summary(unemployed_logit0, cluster = "CBSA10")
```
```{r}
# without transformation 
unemployed_linear0 <- felm(unemployed ~ count_cbsa|CBSA10 + reg_yr|0|CBSA10,data=df_sample_unemployed_full)
summary(unemployed_linear0)
```
```{r}
# without transformation 
unemployed_linear1 <- felm(unemployed ~ count_cbsa + age + age_sqrd + never_married + edu+white|
                             CBSA10+reg_yr|0|CBSA10,data=df_sample_unemployed_full)
summary(unemployed_linear1)
```

### control for industry
```{r}
df_sample_unemployed <- df_sample %>% drop_na(c(count_cbsa, age,  age_sqrd, white,
                                              never_married, IV_ct, CBSA10, edu,
                                              reg_yr, unemployed, industry, ind_yr))
```

```{r}
# without transformation 
unemployed_logit0  <- feglm(unemployed ~ count_cbsa | CBSA10 + reg_yr + ind_yr, family=binomial(), data=df_sample_unemployed)
summary(unemployed_logit0, cluster = "CBSA10")
```

```{r}
# with inverse hyperbolic sine transformation 
unemployed_logit0_asinh  <- feglm(unemployed ~ count_cbsa_asinh | CBSA10 + reg_yr+ ind_yr, 
                                family=binomial(), data=df_sample_unemployed)
summary(unemployed_logit0, cluster = "CBSA10")
```


```{r}
# without transformation 
unemployed_linear0 <- felm(unemployed ~ count_cbsa|CBSA10 + reg_yr+ ind_yr|0|CBSA10,data=df_sample_unemployed)
summary(unemployed_linear0)
```

```{r}
# without transformation 
unemployed_logit1 <-feglm(unemployed ~ count_cbsa + age + age_sqrd + never_married + edu+white | CBSA10 +reg_yr+ ind_yr, family=binomial(), data=df_sample_unemployed)
summary(unemployed_logit1, cluster = "CBSA10")
```

```{r}
# without transformation 
unemployed_linear1 <- felm(unemployed ~ count_cbsa + age + age_sqrd + never_married + edu+white|
                             CBSA10+reg_yr+ind_yr|0|CBSA10,data=df_sample_unemployed)
summary(unemployed_linear1)
```
```{r}
# with transformation 
unemployed_linear1_asinh <- felm(unemployed ~ count_cbsa_asinh + age + age_sqrd + never_married + edu+white|CBSA10+reg_yr+ind_yr|0|CBSA10,data=df_sample_unemployed)
summary(unemployed_linear1)
```



```{r}
stargazer(employed_linear1, temp_off_linear1, unemployed_linear1, type="latex")
```


## IV

#### employed
##### discrete
```{r}


employed1_iv2_d <- felm(employed ~  age + age_sqrd + never_married + edu+white|
                        CBSA10+reg_yr+ind_yr|(count_cbsa~IV_d_ct)|CBSA10,
                      data=df_sample_employed)
summary(employed1_iv2_d)
waldtest(employed1_iv2_d$stage1, ~IV_d_ct)
```
##### continuous
```{r}

employed1_iv2 <- felm(employed ~  age + age_sqrd + never_married + edu+white|
                        CBSA10+reg_yr+ind_yr|(count_cbsa~IV_ct)|CBSA10,
                      data=df_sample_employed)
summary(employed1_iv2)
waldtest(employed1_iv2$stage1, ~IV_ct)
```




#### temp-off
##### discrete
```{r}


temp1_iv2_d <- felm(temp_off ~  age + age_sqrd + never_married + edu+white|
                        CBSA10+reg_yr+ind_yr|(count_cbsa~IV_d_ct)|CBSA10,
                      data=df_sample_temp_off)
summary(temp1_iv2_d)
waldtest(temp1_iv2_d$stage1, ~IV_d_ct)
```
##### continuous
```{r}

temp1_iv2 <- felm(temp_off ~  age + age_sqrd + never_married + edu+white|
                        CBSA10+reg_yr+ind_yr|(count_cbsa~IV_ct)|CBSA10,
                      data=df_sample_temp_off)
summary(temp1_iv2)
waldtest(temp1_iv2$stage1, ~IV_ct)
```
#### unemployed
##### discrete
```{r}

unemployed1_iv2_d <- felm(unemployed ~  age + age_sqrd + never_married + edu+white|
                        CBSA10+reg_yr+ind_yr|(count_cbsa~IV_d_ct)|CBSA10,
                      data=df_sample_unemployed)
summary(unemployed1_iv2_d)
waldtest(unemployed1_iv2_d$stage1, ~IV_d_ct)
```
##### continuous
```{r}
unemployed0_iv1 <- felm(count_cbsa ~ IV_ct |CBSA10+reg_yr+ind_yr|0|CBSA10,
                      data=df_sample_unemployed)
summary(unemployed0_iv1)

unemployed1_iv1 <- felm(count_cbsa ~ IV_ct + age + age_sqrd + never_married + edu+white|
                        CBSA10+reg_yr+ind_yr|0|CBSA10,data=df_sample_unemployed)
summary(unemployed1_iv1)


unemployed1_iv2 <- felm(unemployed ~  age + age_sqrd + never_married + edu+white|
                        CBSA10+reg_yr+ind_yr|(count_cbsa~IV_ct)|CBSA10,
                      data=df_sample_unemployed)
summary(unemployed1_iv2)
waldtest(unemployed1_iv2$stage1, ~IV_ct)
```






# hous_production

```{r}
df_sample_hous_production <- df_sample %>% drop_na(c(count_cbsa, age,  age_sqrd,white, 
                                              never_married, IV_ct, CBSA10, edu, 
                                              reg_yr, hous_production))
```

## baseline

```{r}
# without transformation 
hous_production_logit0  <- feglm(hous_production ~ count_cbsa | CBSA10 + reg_yr, family=binomial(), data=df_sample_hous_production)
summary(hous_production_logit0, cluster = "CBSA10")
```

```{r}
# with inverse hyperbolic sine transformation 
hous_production_logit0_asinh  <- feglm(hous_production ~ count_cbsa_asinh | CBSA10 + reg_yr, 
                                family=binomial(), data=df_sample_hous_production)
summary(hous_production_logit0, cluster = "CBSA10")
```


```{r}
# without transformation 
hous_production_linear0 <- felm(hous_production ~ count_cbsa|CBSA10 + reg_yr|0|CBSA10,data=df_sample_hous_production)
summary(hous_production_linear0)
```

```{r}
# without transformation 
hous_production_logit1 <-feglm(hous_production ~ count_cbsa + age + age_sqrd + never_married + edu+white | CBSA10 + reg_yr, family=binomial(), data=df_sample_hous_production)
summary(hous_production_logit1, cluster = "CBSA10")
```

```{r}
# without transformation 
hous_production_linear1 <- felm(hous_production ~ count_cbsa + age + age_sqrd + never_married + edu+white|CBSA10+reg_yr|0|CBSA10,data=df_sample_hous_production)
summary(hous_production_linear1)
```

## IV
### discrete
```{r}


hous1_iv2_d <- felm(hous_production ~  age + age_sqrd + never_married + edu+white|
                        CBSA10+reg_yr|(count_cbsa~IV_d_ct)|CBSA10,
                      data=df_sample_hous_production)
summary(hous1_iv2_d)
waldtest(hous1_iv2_d$stage1, ~IV_d_ct)
```

```{r}
summary(felm(count_cbsa ~ IV_ct |CBSA10+reg_yr|0|CBSA10,
                      data=df_sample_hous_production))
```

```{r}
ggplot(aes(x=IV_ct, y=count_cbsa), data=df_sample_hous_production)+geom_point()
```

### continuous
```{r}
hous0_iv1 <- felm(count_cbsa ~ IV_ct |CBSA10+reg_yr|0|CBSA10,
                      data=df_sample_hous_production)
summary(hous0_iv1)

hous1_iv1 <- felm(count_cbsa ~ IV_ct + age + age_sqrd + never_married + edu+white|
                        CBSA10+reg_yr|0|CBSA10,data=df_sample_hous_production)
summary(hous1_iv1)

hous1_iv2 <- felm(hous_production ~  age + age_sqrd + never_married + edu+white|
                        CBSA10+reg_yr|(count_cbsa~IV_ct)|CBSA10,
                      data=df_sample_hous_production)
summary(hous1_iv2)

waldtest(hous1_iv2$stage1, ~IV_ct)
```



# hours worked
## baseline

```{r}
df_sample_hrs_work <- df_sample %>% drop_na(c(count_cbsa, age,  age_sqrd, white,edu, 
                                              never_married, IV_ct, IV_d_ct, CBSA10, 
                                              reg_yr, hrs_work, industry, ind_yr,))
```



```{r}
# without transformation 
hrs_work0 <- felm(hrs_work ~ count_cbsa|CBSA10+reg_yr+ind_yr|0|CBSA10,data=df_sample_hrs_work)
summary(hrs_work0)
```
```{r}
# with transformation 
hrs_work0_asinh <- felm(hrs_work ~ count_cbsa_asinh|CBSA10+reg_yr+ind_yr|0|CBSA10,data=df_sample_hrs_work)
summary(hrs_work0_asinh)
```

```{r}
# without transformation 
hrs_work1 <- felm(hrs_work ~ count_cbsa + age + age_sqrd +white+ never_married + edu|CBSA10+reg_yr+ind_yr|0|CBSA10,data=df_sample_hrs_work)
summary(hrs_work1)
```

```{r}
# with transformation 
hrs_work1_asinh <- felm(hrs_work ~ count_cbsa_asinh + age + age_sqrd + never_married + edu+white|CBSA10+reg_yr+ind_yr|0|CBSA10,data=df_sample_hrs_work)
summary(hrs_work1_asinh)
```
```{r}
stargazer(hous_production_linear0, hous_production_linear1,type='text')
```

```{r}
stargazer(hrs_work0,hrs_work1, type='text')

```

## IV
### discrete
```{r}


hrs_work1_iv2_d <- felm(hrs_work ~  age + age_sqrd + never_married + edu+white|
                        CBSA10+reg_yr+ind_yr|(count_cbsa~IV_d_ct)|CBSA10,
                      data=df_sample_hrs_work)
summary(hrs_work1_iv2_d)
waldtest(hrs_work1_iv2_d$stage1, ~IV_d_ct)
```

```{r}
summary(felm(count_cbsa ~ IV_ct |CBSA10+reg_yr+ind_yr|0|CBSA10,
                      data=df_sample))
```

```{r}
ggplot(aes(x=IV_d_ct, y=count_cbsa), data=df_sample_hrs_work)+geom_point()
ggplot(aes(x=IV_ct, y=count_cbsa), data=df_sample_hrs_work)+geom_point()
```

### continuous

```{r}

hrs_work1_iv2 <- felm(hrs_work ~  age + age_sqrd + never_married + edu+white|
                        CBSA10+reg_yr+ind_yr|(count_cbsa~IV_ct)|CBSA10,
                      data=df_sample_hrs_work)
summary(hrs_work1_iv2)

waldtest(hrs_work1_iv2$stage1, ~IV_ct)
```

# occupation mobility
## baseline

```{r}
df_sample_occ <- df_sample %>% drop_na(c(count_cbsa, age,  age_sqrd, white,
                                              never_married, IV_ct, IV_d_ct, CBSA10, edu, 
                                              reg_yr, occupation_mobility, industry, ind_yr))
```



```{r}
# without transformation 
occ0 <- felm(occupation_mobility ~ count_cbsa|CBSA10+reg_yr+ind_yr|0|CBSA10,data=df_sample_occ)
summary(occ0)
```
```{r}
# with transformation 
occ0_asinh <- felm(occupation_mobility ~ count_cbsa_asinh|CBSA10+reg_yr+ind_yr|0|CBSA10,data=df_sample_occ)
summary(occ0_asinh)
```

```{r}
# without transformation 
occ1 <- felm(occupation_mobility ~ count_cbsa + age + age_sqrd +white+ never_married + edu|CBSA10+reg_yr+ind_yr|0|CBSA10,data=df_sample_occ)
summary(occ1)
```

```{r}
# with transformation 
occ1_asinh <- felm(occupation_mobility ~ count_cbsa_asinh + age + age_sqrd + never_married + edu+white|CBSA10+reg_yr+ind_yr|0|CBSA10,data=df_sample_occ)
summary(occ1_asinh)
```


```{r}
stargazer(occ0,occ1, type='text')

```

## IV
### discrete
```{r}

occ1_iv2_d <- felm(occupation_mobility ~  age + age_sqrd + never_married + edu+white|
                        CBSA10+reg_yr+ind_yr|(count_cbsa~IV_d_ct)|CBSA10,
                      data=df_sample_occ)
summary(occ1_iv2_d)
waldtest(occ1_iv2_d$stage1, ~IV_d_ct)
```

```{r}
summary(felm(count_cbsa ~ IV_ct |CBSA10+reg_yr+ind_yr|0|CBSA10,
                      data=df_sample))
```

```{r}
ggplot(aes(x=IV_d_ct, y=count_cbsa), data=df_sample_occ)+geom_point()
ggplot(aes(x=IV_ct, y=count_cbsa), data=df_sample_occ)+geom_point()
```
### continuous
```{r}

occ1_iv2 <- felm(occupation_mobility ~  age + age_sqrd + never_married + edu+white|
                        CBSA10+reg_yr+ind_yr|(count_cbsa~IV_ct)|CBSA10,
                      data=df_sample_occ)
summary(occ1_iv2)

waldtest(occ1_iv2$stage1, ~IV_ct)
```


# occupation change direction
## baseline

```{r}
df_sample_occ_change <- df_sample %>% drop_na(c(count_cbsa, age,  age_sqrd, white,edu, 
                                              never_married, IV_ct, IV_d_ct, CBSA10, 
                                              reg_yr, occ_change, industry, ind_yr))
```



```{r}
# without transformation 
occ_change1 <- felm(occ_change ~ count_cbsa + age + age_sqrd +white+ never_married + edu|CBSA10+reg_yr+ind_yr|0|CBSA10,data=df_sample_occ_change)
summary(occ_change1)
```

```{r}
# with transformation 
occ_change1_asinh <- felm(occ_change ~ count_cbsa_asinh + age + age_sqrd + never_married + edu+white|CBSA10+reg_yr+ind_yr|0|CBSA10,data=df_sample_occ_change)
summary(occ_change1_asinh)
```


```{r}
stargazer(occ_change0,occ_change1, type='text')

```

## IV
### discrete
```{r}


occ_change1_iv2_d <- felm(occ_change ~  age + age_sqrd + never_married + edu+white|
                        CBSA10+reg_yr+ind_yr|(count_cbsa~IV_d_ct)|CBSA10,
                      data=df_sample_occ_change)
summary(occ_change1_iv2_d)
waldtest(occ_change1_iv2_d$stage1, ~IV_d_ct)
```

```{r}
summary(felm(count_cbsa ~ IV_ct |CBSA10+reg_yr+ind_yr|0|CBSA10,
                      data=df_sample))
```

```{r}
ggplot(aes(x=IV_d_ct, y=count_cbsa), data=df_sample_occ_change)+geom_point()
ggplot(aes(x=IV_ct, y=count_cbsa), data=df_sample_occ_change)+geom_point()
```
##### continuous
```{r}
occ_change0_iv1 <- felm(count_cbsa ~ IV_ct |CBSA10+reg_yr+ind_yr|0|CBSA10,
                      data=df_sample_occ_change)
summary(occ_change0_iv1)

occ_change1_iv1 <- felm(count_cbsa ~ IV_ct + age + age_sqrd + never_married + edu+white|
                        CBSA10+reg_yr+ind_yr|0|CBSA10,data=df_sample_occ_change)
summary(occ_change1_iv1)

occ_change1_iv2 <- felm(occ_change ~  age + age_sqrd + never_married + edu+white|
                        CBSA10+reg_yr+ind_yr|(count_cbsa~IV_ct)|CBSA10,
                      data=df_sample_occ_change)
summary(occ_change1_iv2)

waldtest(occ_change1_iv2$stage1, ~IV_ct)
```

#Summarize

```{r}
stargazer(employed_linear1,temp_off_linear1,unemployed_linear1, type="latex")
```

```{r}
stargazer(hous_production_linear1, hrs_work1, occ1, occ_change1,type="latex")
```


```{r}
stargazer(employed1_iv2,temp1_iv2, unemployed1_iv2, type="latex")
```
```{r}
waldtest(employed1_iv2$stage1,~IV_ct)
summary(employed1_iv2$stage1)
waldtest(employed1_iv2_d$stage1,~IV_d_ct)
summary(employed1_iv2_d$stage1)
```

```{r}
stargazer(employed1_iv2_d,temp1_iv2_d, unemployed1_iv2_d, type="latex")
```

```{r}
stargazer(hous1_iv2, hrs_work1_iv2, occ1_iv2, occ_change1_iv2,type="latex")
```

```{r}
stargazer(hous1_iv2_d, hrs_work1_iv2_d, occ1_iv2_d, occ_change1_iv2_d,type="latex")
```
```{r}
waldtest(hous1_iv2$stage1,~IV_ct)
summary(hous1_iv2$stage1)
waldtest(hous1_iv2_d$stage1,~IV_d_ct)
summary(hous1_iv2_d$stage1)
```


```{r}
waldtest(hrs_work1_iv2$stage1,~IV_ct)
summary(hrs_work1_iv2$stage1)
waldtest(hrs_work1_iv2_d$stage1,~IV_d_ct)
summary(hrs_work1_iv2_d$stage1)
```


```{r}
waldtest(occ1_iv2$stage1,~IV_ct)
summary(occ1_iv2$stage1)
waldtest(occ1_iv2_d$stage1,~IV_d_ct)
summary(occ1_iv2_d$stage1)
```